HMMotion: Using tracking data to predict coverage strategies in American Football

### 2025-01-07 README.Rmd
updating README

This is the github repository for the corresponding submission to the NFL Big Data Bowl 2024 competition on Kaggle. The full notebook can be viewed [here](https://www.kaggle.com/code/rouvenmichels/hmmotion-using-tracking-data-to-predict-coverage).

@@

>>>>

This is the github repository for the corresponding submission to the NFL Big Data Bowl 2025 competition on Kaggle. The full notebook can be viewed [here](https://www.kaggle.com/code/rouvenmichels/hmmotion-using-tracking-data-to-predict-coverage).

@@

In this project, we focused on incorporating pre-snap motion information into the prediction of the coverage scheme, i.e. man or zone-coverage. Specifically, we developed a hidden Markov model (HMM) to infer the latent guarding assignments based on the movement of the defenders in response to all offenders. We show that incorporating the informaton obtained from decoding the hidden guarding assignments can improve the predictive power of the coverage scheme.
